---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(badger)
```

# CellScape

`r badge_bioc_release("cellscape", "green")`
`r badge_bioc_download_rank("cellscape")`
`r badge_bioc_download("cellscape", "month", "green")`


CellScape is a visualization tool for integrating single cell phylogeny with genomic content to clearly display evolutionary progression and tumour heterogeneity. 

## Installation 

To install CellScape, type the following commands in R:

```{r, eval=FALSE}
# try http:// if https:// URLs are not supported
if (!requireNamespace("BiocManager", quietly = TRUE)) {
  install.packages("BiocManager")
}
BiocManager::install("cellscape")
```

## Examples 

Run the examples by: 

```{r, eval=FALSE}
example("cellscape")
```

## Documentation 

To view the documentation for CellScape, type the following command in R:

```{r, eval=FALSE}
?cellscape
```

or:

```{r, eval=FALSE}
browseVignettes("cellscape")
```

## Citation

- [Smith, Maia A., et al. "E-scape: interactive visualization of single-cell phylogenetics and cancer evolution." ***Nature Methods*** 14.6 (2017): 549-550.](https://www.nature.com/articles/nmeth.4303)

## Maintainer

- [Shixiang Wang](https://github.com/ShixiangWang)
